Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-19 mu/article/article.tex
Changing working station

\subsection{Fixing spin}\label{sec:theory-fixspin}
Considering that we have 2D structures we can fix the spin direction along the
$x$, $y$, and $z$ Cartesian coordinates and then define the magnitude of the
spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)|$ in a fixed angle $\gamma_{\mathrm{b}}(\omega,\alpha)$ as
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)| 
&=
\sqrt{
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2}\ +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2}\ 
}, 
\label{eq:vs-mag}
\\
\gamma_{\mathrm{b}} (\omega,\alpha)
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
\label{eq:gamma-ang}
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ axis.

@@

In a similar way we can fix the velocity in the $xy$ plane
along $x$ and $y$ directions and define $|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ as
\begin{align}
|\mathcal{V}^{\mathrm{a}}&(\omega,\alpha)| = \nonumber \\
&\sqrt { 
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} 
},
\label{eq:vv-mag}
\end{align}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta_{\mathrm{a}}  (\omega,\alpha)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
{|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi_{\mathrm{a}} (\omega,\alpha)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

@@

We calculated the self-consistent ground state and the Kohn-Sham states using
density functional theory in the local density approximation (DFT-LDA) with a
planewave basis using the ABINIT code \cite{gonzeCPC09}. We used 
Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented in Eq.
\eqref{eq:mu}.
% 
It is known that using DFT-LDA to calculate the electronic structure of
materials predict a different band gap than the obtained experimentally. A
correction for the band gap energy value can be calculated by other 
\emph{ab-initio} methods such as the GW approximation \cite{onidaRMP02} but this
is outside the scope of this paper.
% 
The convergence parameters for the calculations of our results corresponding to
the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
40\,Ha, respectively. The energy eigenvalues and matrix elements were calculated
using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the irreducible
Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV and 0.088\,eV,
respectively for the \emph{alt} and \emph{up} structures.

>>>>

\subsection{Fixing spin}\label{sec:theory-fixspin}
Considering that we have 2D structures, one of the options is fix the spin along
the $x$, $y$, or $z$ Cartesian coordinates. We define the magnitude of the spin
velocity with spin polarization along the $\mathrm{b}$ direction as 
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)| 
&=
\sqrt{
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2}\ +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2}\ 
}, 
\label{eq:vs-mag}
\end{align}
and the angle at which the spin velocity is directed as
\begin{align}
\gamma_{\mathrm{b}} (\omega,\alpha)
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
\label{eq:gamma-ang}
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ Cartesian coordinate.

@@

In a similar way we can fix the velocity on the $xy$ plane along $x$ or $y$
Cartesian coordinate and then define the magnitude of the spin velocity directed
along the $\mathrm{a}$ direction as
\begin{align}
|\mathcal{V}^{\mathrm{a}}&(\omega,\alpha)| = \nonumber \\
&\sqrt { 
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} .
},
\label{eq:vv-mag}
\end{align}
Then, the spin direction depends of the components of the previous equation and
so we define the spin polar and azimuthal angles as
\begin{align}
\theta_{\mathrm{a}}  (\omega,\alpha)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
{|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi_{\mathrm{a}} (\omega,\alpha)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}
where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the positive to the
negative $z$ Cartesian coordinate and $\varphi_{\mathrm{a}}(\omega,\alpha)$ is
measured on the $xy$ plane in the counter-clockwise direction from the positive
$x$ Cartesian coordinate.

@@

We calculated the self-consistent ground state and the Kohn-Sham states using
density functional theory in the local density approximation (DFT-LDA) with a
planewave basis using the ABINIT code \cite{gonzeCPC09}. We used 
Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented in Eq.
\eqref{eq:mu}.
% 
The convergence parameters for the calculations of our results corresponding to
the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
40\,Ha, respectively. The energy eigenvalues and matrix elements for the
\emph{up} ad \emph{alt} structures were calculated using 14452 $\mathbf{k}$
points and 8452 $\mathbf{k}$ points in the irreducible Brillouin zone (IBZ)
presenting LDA energy band gaps of 0.72\,eV and 0.088\,eV, respectively.
% 
We notice that within DFT, the LDA is only one of other possible methods that
can be used to determine the electronic structure of materials. Recent
investigations on graphene show some of the differences in calculated values
from several of these methods\cite{karamanisJPCC15,botelloACR14}. We note that
the LDA is as good as these other approaches. It is also known that the DFT
calculations predict a band gap for the material that differs from experiment.
This can be corrected using other \emph{ab initio} techniques, such as the GW
approximation\cite{onidaRMP02}, but this calculation has a very high
computational cost and is out of the scope in this paper. Even so, DFT still
remains as an effective and useful tool for computing diverse properties derived
from the electronic band structure.
